### 2021-04-17 nih/specific_aims.tex
Revise specific aims

@@

>>>>

The objective of this proposal is to reveal and analyze cognitive representation of tinnitus percepts
through a novel compressive sensing-based reverse correlation framework.

@@

Our long-term goal is to efficiently uncover effective representations of tinnitus percepts to inform diagnosis and treatment
and to explain variability in tinnitus experience.
Our guiding hypothesis is that reverse correlation will produce individualized, unbiased, high-dimensional cognitive representations of tinnitus percepts
and that we can optimize reverse correlation to require fewer samples using signal reconstruction techniques.
[RATIONALE]
We will test our central hypothesis and attain our objective via the following specific aims:
